\LaTeX is great

### 2014-01-26 misc/mwe.tex
add rest of tex

\chapter{Molybdenum Oxides}

\section{Introduction}

Molybdenum oxides \ce{MoO3} crystallizes in three phases, orthorhombic $\alpha$-\ce{MoO3}, monoclinic $\beta$-\ce{MoO3} and the metastable hexagonal h-\ce{MoO3}.\citep{Deb1968,Fibers2007} $\alpha$-\ce{MoO3} phase exhibits anisotropic structure with strong bonding along [001] and [100] direction while Van der Waals interaction along [010] direction.\cite{He2003} Due to this unique structure, \ce{MoO3} was found to have several important properties and a wide range of technological applications, such as electrochromism and photochromism,\cite{Yao1992} lubricants,\cite{Sheehan1996} photocatalysts,\cite{Chen2010} and gas sensor, including \ce{CO},\cite{Comini2005} \ce{NO2},\cite{Taurino2006} \ce{H2}\cite{Sha2009} and ethanol.\cite{Choopun} Moreover, other features arise when nanoscale \ce{MoO3} is specifically prepared, for instance, field emission.\citep{Li2002d,Zhou2003b}  As a layered hosting material, \ce{MoO3} can be further modified by intercalating with alkaline ions\citep{Spahr1995,Li2006b,Hu2011} and even divalent ion\cite{Sian2005}. This structural richness have enabled improved performance in Li-ion\cite{Mai2007} and sodium-ion battery.\cite{Hariharan2013} In combination with \ce{TiO2} forming a core-shell structure, these nanoparitcles are reported to lower the photoabsorption energy of \ce{TiO2}.\cite{Elder2000} When combined with Ag as layered structure, transparent conducting behavior was observed.\cite{Nguyen2012} In addition, \ce{MoO3} is a good precursor for preparing other useful materials, such as \ce{MoS2} fullerenes\cite{Li2003c}, and few layer \ce{MoS2}.\cite{Lin2012}  It will also be an important member of the Van der Waals heterostructures.\cite{Geim2013}

It may be considered as built up of chains of \ce{MoO4} tetrahedra connected by the sharing of two oxygen corners with two neighbouring tetrahedra in $c$ axis. The infinite chains of \ce{MoO4} tetrahedra from half-layers in the $ac$ plane. Two half-layers, which are stapled along $b$ axis, build up one \ce{MoO3} layer. When the two more distant oxygen are included for one molybdenum atom, the coordination can be regards a sixfold, i.e,, the layered structure consisting of zig-zag rows of edge-sharing \ce{MoO6} octahedra, while the rows are mutually connected by corners.\cite{Itoh2001a}

on \ce{MoO3} reviews.\cite{He2003}

\citeauthor{Chithambararaj2013} prepared hexagonal \ce{MoO3} nanocrystal via hydrothermal method  and demonstrated the photodegradation of MB under visible light.\cite{Chithambararaj2013} The efficiency dependence on catalysis/dye ratio, light intensity and temperature was studied. h-\ce{MoO3} was mostly synthesized using solution methods, where \ce{NH4+} and \ce{OH.} were possible structure directing and stable agents. The band gap of h-\ce{MoO3} estimated from diffusion reflection spectrum is $2.8\sim3.0eV$.

Hexagonal phase \ce{MoO3} is readily identified by the XRD pattern (strong peak at $2\theta=20^{\circ}$).

\section{Syntheses Methods}
\subsection{literature review}

\subsection{this work}
\textbf{Substrate treatment.} Silicon substrates(p-$\langle100\rangle$, University Wafers) were first cut into 10mm by 25mm pieces and ultrasonically cleaned with acetone and ethanol for 15 minutes(Branson 1510R-MTH), each followed by blow-drying with nitrogen gas. Then the substrates were selectively treated in an oxygen plasma cleaning apparatus(Kurt J Lesker: Plasma-Preen 862, 2Torr) for 3 minutes to increase the wettability. The substrates without plasma cleaning were rendered as hydrophobic. Finally, the substrate was drop-cast 54 $\mu$L 10 mM \ce{NaOH} (or \ce{KI}, \ce{Na2CO3}) and naturally left dry in a convection hood with a flask cover above. Other alkaline ions-containing substrates, such as glass (Fisher Scientific, microscope slide, 12-549) and indium tin oxide (ITO) coated glass(Delta Technologies, 25\si{\ohm}), were cleaned by the same routine except the absence of plasma cleaning and subsequent aqueous solution dipping. Mica was cleaved right before growth without other treatment.

\textbf{Synthesis.} In a typical synthesis, molybdenum powders were loaded into the uniform heating zone and the sealed chamber was first pumped down to 10 mTorr. Then oxygen flow varying between 0.1 sccm to 10 sccm (standard cubic centimeter per minute) was admitted from upstream inlet. With 10 sccm UHP Ar(99.999\%)as carrier gas, the overall pressure reached about 200 mTorr. The heating temperature was ramped up to 800 \si{\degreeCelsius} in 30 minutes and lasted for 15 to 120 minutes. Then the heating power was turned off and the chamber was allowed to naturally cool down to room temperature. The receiving substrate was placed in downstream location where the temperature was about 400 to 670 \si{\degreeCelsius} according to open air temperature profile. To observe the formation of droplets, clean silicon substrate was coated with 9 nm molybdenum film using a magnetron sputter(Desk IV TSC, Denton Vacuum), followed by \ce{NaOH} dipping as described before. Then the substrate was placed into chamber for growth, where all the parameters remained unchanged except the absence of Mo powder source.

\section{Discussion}

In vapor synthesis process, two growth mechanism exists: VS and VLS. VS process is widely accepted for the growth of \ce{MoO3}. Yet we caution that synthesis conditions should be scrutinized to determine the exact mechanism. \citeauthor{Li2002c} suggested a VS mechanism at 700 \si{\degreeCelsius} and VLS at 750 \si{\degreeCelsius} and higher.\cite{Li2002c} \citeauthor{Fibers2007} proposed a modified VS mechanism probably because the deposition occurs on \ce{Al2SiO5} with possible \ce{Al_{0.95}SiNa_{0.06}O_x} involved. Therefore temperature and possible impurity could potentially alter the growth mechanism. We divide the growth results into two categories: on Si substrate and on non-Si substrate to describe them respectively.

\subsection{Growth on Si substrates}

Mo began to be oxidized into \ce{MoO3} at 500 \si{\degreeCelsius}, \ce{MoO3} vapor pressure began to increase rapidly above 700 \si{\degreeCelsius}. \cite{Margrave1967} And the MP of \ce{MoO3} is reported as 795 \si{\degreeCelsius}. With these facts in mind, we design the experimental parameters as listed in Table.~\ref{tab:mooxsi}. We should point out that these parameters are selected and optimized from a wide range of combinations. And when we discuss the influence of one parameter with different values, one should assume other parameters still adapt those listed in Table.~\ref{tab:mooxsi}.

\begin{table}[htb]
\centering
\caption{Growth conditions of \ce{MoO3} on Si}\label{tab:mooxsi}
\begin{tabular}{lcccr}
\toprule
&&&\multicolumn{2}{c}{Flow (sccm)} \\
\cmidrule(l){4-5}
 & Temperature $T_h$ (\si{\degreeCelsius}) & Pressure  & Ar & \ce{O2}  \\
\midrule
typical values  & 800    & 200mTorr & 10 & 10  \\
\end{tabular}
\end{table}

The growth layout is schematically shown in Fig.~\ref{fig:mooxgrowth}. Notice that on the horizontal axis of temperature, zero inch is defined at the upstream edge of furnace. To facilitate discussion and provide a tight context, we define the position of substrate as the coordinate of its upper-stream edge along this temperature axis (i.e. the substrate location is 7 inch in Fig.~\ref{fig:mooxgrowth}). The usual length of Si substrate is 1 inch. When positioned at 7 inch, it is then located in a temperature range of $650 \sim 350$ \si{\degreeCelsius}.

\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{CVD_and_temp_MoO3.jpg}
\caption[Growth setup of \ce{MoO3}]{Chemical vapor system and its temperature profile. The triangular labels $\blacktriangledown$ were measured points at ambient pressure. The nominal substrates temperature were estimated from interpolation data.}
\label{fig:mooxgrowth}
\end{figure}

From previous works,\cite{predeep2011} we found that with $T_h = 600$ and substrate placed at 6.5 inches, microflakes was found at the high temperature edge of Si, suggesting the nucleation already started.\footnote{020510 batch} When flow of oxygen was gradually reduced, diminished size of micro-flake was observed at the same location of substrates. This results indicated the rate-determining step is diffusion when oxygen flow was in the range of 2 sccm to 0.5 sccm.\footnote{(31210-31510 batches)} We also found the deposition amount on a particular location of the substrate is not linearly proportional to the growth time, i.e., the growth at upper stream edge first increase then decrease. This is not surprising when considering the temperature field requires some time to become synchronized as depicted in Fig.~\ref{fig:mooxgrowth}. Using conditions in Table.~\ref{tab:mooxsi} and 1 hr growth, we observed the typical micro-flakes morphologies as shown in Fig.~\ref{fig:mosisem}. Most flakes exhibit rectangular shape, with average thickness of one micron, standard deviation $\sigma_D=0.34\mu m$.

\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:mosem1}\includegraphics[width=0.45\textwidth]{mosemsi_a}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:mosem2}\includegraphics[width=0.45\textwidth]{mosemsi_b}}
\caption[Representative morphologies of \ce{MoO3} on Si]{SEM images of representative depositions of \ce{MoO3} on Si. (a)Low magnification. (b) High magnification. }
\label{fig:mosisem}
\end{figure}

This rectangular shape implies the boundary plane along growth direction (long axis) is (001), in consistency with previous experimental\cite{Zeng1998,Li2002b} and theoretical\cite{Firment1983,Cora1997} studies. We also observed different shapes, i.e., elongated hexagonal using similar growth conditions. This is not an indication of different growth mode. It is a normal thermodynamic fluctuation. In fact, (201), (101) and (102) planes have all been observed as terminating planes.\cite{Zeng1998} The stacking rate of \ce{MoO6} octahedra along a and c axis could develop some other ratio. And the coexistence of different planes in one growth suggests the similarity of free surface energies.

\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:moxrd}\includegraphics[width=0.45\textwidth]{xrd_moo3}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:moram}\includegraphics[width=0.45\textwidth]{raman_moo3}}
\caption[Crystalline phase characterization of \ce{MoO3} on Si]{(a) XRD pattern and (b) Raman spectrum of typical \ce{MoO3} on Si, $\lambda_{ex} = 532nm$.}
\label{fig:mooxch}
\end{figure}

As shown in Fig.~\ref{fig:mooxch}, the crystal structures and phase of as-synthesized samples were examined by XRD and Raman. The XRD pattern (Fig.~\ref{fig:moxrd}) is readily indexed to the orthorhombic phase of \ce{MoO3} (ICDD PDF 05-0508, \emph{a}=3.9628\AA, \emph{b}=13.855\AA, \emph{c}=3.6964\AA). The space group is $D_{2h}^{16}(Pbnm)$. This crystal structure is indeed a unique example among transition metal oxides, representing a transitional stage between tetrahedra and octahedral coordination.\cite{Itoh2001a} The strongest peak index is (110), suggesting the orientation of \ce{MoO3} is not parallel to the substrate, which is consistent with the morphology displayed in Fig.~\ref{fig:mosem1}. In contrast, we shall see a different scenario in Section.~\ref{sec:nasi}, where the orientation is changed. The Raman spectrum of as-synthesized specimens also closely matches \ce{MoO3} features in previous studies.\cite{Dixit1986,Silveira2012} During m-Raman measurement, the laser spot was carefully focused onto the plates and several inspections on different positions were observed to ensure the reproductivity of spectra data. As shown in Fig.~\ref{fig:moram}, 14 distinct bands were well resolved. The 284 \si{cm^{-1}} peak represents the wagging mode for double bond \ce{O=Mo=O}. The 337 and 380  \si{cm^{-1}} peaks are assigned to \ce{O-Mo-O} bending and scissoring modes. The 199 \si{cm^{-1}} peak and two other weaker peaks at 218 and 247 \si{cm^{-1}} represent \ce{O=Mo=O} $B_{2g}$ twist, $A_g$ chain mode and \ce{O=Mo=O} $B_{3g}$ twist mode, respectively.    667 \si{cm^{-1}} peak is assigned to triply coordinated oxygen stretching model resulting from edge-shared oxygen in common to three octahedral. The 819 \si{cm^{-1}} peak is from doubly coordinated oxygen stretching mode arising from corner-shared oxygen between two octahedral. The 996 \si{cm^{-1}} peak comes from unshared oxygen stretching mode.\cite{Siciliano2009} The assignment is summarized in Table.~\ref{tab:moram}.

\begin{table}[htb]
\centering
\caption{Experimental Raman peaks (\si{cm^{-1}}) assignment of \ce{MoO3} on Si.\cite{Eda1992,Siciliano2009}}\label{tab:moram}
\begin{tabular}{llcll}
\toprule
this work & Sym.       &          & Assignment &   \\
\midrule
117      & $B_{2g}$    &           & $T_c$  & RCM  \\
129      & $B_{3g}$    &           & $T_c$  & RCM  \\
158      & $A_g/B_{1g}$&           & $T_b$  & RCM  \\
199      & $B_{2g}$    & $\tau$    & \ce{O=Mo=O}  & twist  \\
218      & $A_g$       &           & $R_c$     & RCM  \\
247      & $B_{3g}$    & $\tau$    & \ce{O=Mo=O}  & twist  \\
284      & $B_{2g}$    &           & \ce{O=Mo=O}  & wag  \\
292      & $B_{3g}$     & $\delta$ & \ce{O=Mo=O}  & wag  \\
337      & $A_g,B_{1g}$ & $\delta$ & \ce{O-Mo-O} & bend  \\
380      & $B_{1g}$     & $\delta$ & \ce{O-Mo-O}  & scissor  \\
474      & $A_g$        & $\nu_{as}$ & \ce{O-Mo-O}  & stretch,bend  \\
667      & $B_{2g},B_{3g}$ & $\nu_{as}$  & \ce{O-Mo-O}  & stretch  \\
819      & $A_g$        & $\nu_{as}$  & \ce{O=Mo}  & stretch  \\
996      & $A_g$         & $\nu_{as}$  & \ce{O=Mo}  & stretch  \\
\bottomrule
\end{tabular}
\end{table}

The growth rates along different crystalline direction of \ce{MoO3} are presumably determined by the free surface energy. In other words, the migration barrier of adatoms on (010) plane is presumably much lower than that on other low index planes due to the Van der Waals interaction nature along [010] direction.

\subsection{FL}

FL materials attracts intensive research efforts recently. We first use liquid exfoliation method to prepare FL \ce{MoO3}. We then characterized the absorption feature and crystalline structures of the exfoliated \ce{MoO3} using UV-Vis and TEM. Then we calculate the optical contrast of FL \ce{MoO3} on \ce{SiO2}-Si, which serves as a guideline to identify FL \ce{MoO3} using optical microscope.

The exfoliation solution is 30\% isopropanol (IPA) in DI water, which has been proved to work well on other layered compounds.\cite{Halim2013} After 20 minutes sonication, the dispersion is milky. We measured the transmission spectra of this dispersion immediately upon sonication and after 40 hrs for gravity sedimentation, as illustrated in Fig.~\ref{fig:moabs}. The t0 line mainly arises from the scattering of flakes in the dispersion. There are two scattering mechanisms: Rayleigh scattering and Tyndall scattering. Rayleigh scattering, which occurs when particles are comparable to wavelength, is inversely proportional to the fourth power of wavelength; While Tyndall scattering, which occurs when the particles are larger, is inversely proportional to the square of the wavelength. To fully evaluate the true absorbance of the sample itself, one needs to decouple the scattering part from apparent absorbance. Generally we select one part of spectrum and assume it is only caused by scattering. Then a empirical dependence shown in Eq.~\ref{eq:sca2} is used as polynomial fitting model.

@@

\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:moabs}\includegraphics[width=0.45\textwidth]{MoO3-abs}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:mobg}\includegraphics[width=0.45\textwidth]{MoO3-bg}}
\caption[UV-Vis spectra of exfoliated \ce{MoO3}]{(a) UV-Vis absorbance spectra of exfoliated \ce{MoO3}. Dashed line (t0) represents measurement immediately after sonication, and solid line (t40h) is obtained after sitting for 40 hours. The dot dashed line is reference spectrum of the 30\% IPA. (b) Band gap estimation}
\label{fig:mouv}
\end{figure}

According to the corrected absorbance spectrum, optical band gap can be deduced, which is known as Tauc Plot.\cite{Tauc1972} The procedure is recapitulated here.

\begin{equation}\label{eq:tauc}
 (h\nu \alpha)^{\frac{1}{n}} = B(h\nu - E_g^{opt}),
\end{equation}
where B is a proportional coefficient, $\alpha$ is absorption\footnote{The absorbance $A = 0.4343\alpha*l$, where l is the optical path} and $E_g^{opt}$ is defined as optical band gap. The value n is correlated to the nature of optical transition. For direct allowed transition, n = 1/2; For direct forbidden transition, n = 3/2; For indirect allowed transition, n = 2; And for indirect forbidden transition, n = 3. When the transition nature of sample is not well known, one should apply each to check which one provide the best fit. Depending on the synthesis methods and \ce{MoO3} morphologies, the transition phenomena might vary. On the \ce{MoO3} films, \citeauthor{Bouzidi2003} assumed a direct gap (n = 1/2)\cite{Bouzidi2003} while \citeauthor{Szekeres2002} not.\cite{Szekeres2002} We use n = 2 in this work. We plot $\sqrt{(h\nu \alpha)}$ versus photon energy, and extrapolate the linear part onto $h\nu$ axis. The intercept is used as $E_g^{opt}$ then. Our evaluation and some previous studies is summarized in Table.~\ref{tab:mobg}.

\begin{table}[htb]
\centering
\caption{Optical band gaps of \ce{MoO3}}\label{tab:mobg}
\begin{tabular}{lccr}
\toprule
&\multicolumn{2}{c}{Band gap} \\
\cmidrule(l){2-3}
Reference & value(eV) & orientation & material states\\
\midrule
\cite{Deb1968}   & 2.96  & $E\parallel c_0$ & single crystal\\
\cite{Deb1968}   & 2.80  & $E\perp c_0$ & single crystal \\
\cite{Julien1995} & 2.8$\sim$ 3.2 & NA & films\\
 this work  & 3.1  & NA & nanoflakes\\
\bottomrule
\end{tabular}
\end{table}

An alternative way is a) define $Y = \alpha E=\alpha h\nu$, and obtain $Y' = \frac{\partial Y}{\partial E}$, then b) plot $Y'/Y$ versus $h\nu$. The band gap value can be obtained from the intercept of extrapolated line on photo energy axis.\cite{Choopun} This approach is not difficult to comprehend as long as we notice from Eq.~\ref{eq:tauc}, $Y = B (h\nu - E_g^{opt})^n$ and $Y' = B n(h\nu - E_g^{opt})^{n-1}$.

The dielectric constants\footnote{Not a constant at all, instead, it has complicated dependence on photon energy} ($\epsilon = \epsilon_1 + i*\epsilon_2$) of \ce{MoO3} have been studied in several reports.\cite{Deb1968,Sabhapathi1995,Miyata1996,Abdellaoui1997,Mondragon1999} We extracted $\epsilon_1$ from Ref\cite{Itoh2001a} due to the wide photon energy range utilized. We also notice that $\epsilon_2$ is approximately zero when $h\nu$ is less than 4 eV. Since we are primarily concerned with the optical contrast of FL \ce{MoO3} in visible wavelength region($h\nu < 3$ eV), we obtained refractive indices $n$ from $n = \sqrt{\epsilon_1}$. Due to the orthorhombic phase, \ce{MoO3} exhibit birefringence, that is there are two refractive indices, $n_c$ and $n_a$, as shown in Fig.~\ref{fig:moind}. The refractive index is between $ 2.2\sim 2.4$ along a axis, and $ 2.5\sim 2.8$ along c axis. Comparison to the low frequency dielectric constant ($18.0\pm1$) implies a primarily ionic bonding in \ce{MoO3}.\cite{He2003}

\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:moind}\includegraphics[width=0.45\textwidth]{n_MoO3}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:mocon}\includegraphics[width=0.45\textwidth]{Graph20}}
\caption[Refractive indices of \ce{MoO3}]{(a) Refractive indices of \ce{MoO3} Dashed line is n along $a$ axis while solid line is along $c$ axis. (b) optical contrast mapping of 1L \ce{MoO3} on \ce{SiO2}-Si. The x axis is \ce{SiO2} thickness, y axis is wavelength.It is assumed that the incident light is polarized along c axis of \ce{MoO3}.}
\label{fig:mofl}
\end{figure}

Fig.~\ref{fig:mocon} illustrates the optical contrast mapping of 1L \ce{MoO3} on \ce{SiO2}-Si when the incident light is polarized along c axis of \ce{MoO3}. One can see that .
The refractive indices of Si and \ce{SiO2} within visible wavelengths and MATLAB source code for optical contrast calculation is included in Appendix.

The dimension and phase of exfoliated \ce{MoO3} is examined using TEM. Fig.~\ref{fig:motem} shows the size of exfoliated \ce{MoO3} is about 500 nm. High-resolution TEM (HRTEM) image was taken to assess the \ce{MoO3}. The clearly resolved lattices indicate high crystal quality of \ce{MoO3}.

\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{exf_moo3.jpg}
\caption[TEM images of exfoliated \ce{MoO3}]{(a) TEM image and (b) HRTEM image of FL \ce{MoO3} obtained by liquid sonication method.}
\label{fig:motem}
\end{figure}

\subsection{Growth on non-Si substrates}\label{sec:nasi}

In previous works, \ce{MoO3} deposition on ITO/glass exhibits new morphologies that were not observed on Si substrates, yet the mechanism is not well investigated.\cite{predeep2011} We first repeated the previous growth on ITO/glass, and then found similar deposition phenomena on glass and mica substrates. We suspected that the morphology difference on the substrates employed in this study arises from the compositions difference. Both mica and glass contains alkaline elements which are absent in Si and \ce{SiO2}/Si substrates. We primarily verify this hypothesis by utilizing \ce{NaOH} treated Si substrates and found that the overall morphology almost reproduces that on ITO and mica substrates. We then propose a new growth mechanism based on the VLS process to explain the deposition of \ce{MoO3} on alkaline-ions-containing substrates.

ITO versus NaOH images.

\subsubsection{Na transport}
We estimated the mass transport of sodium ions in silica glass. The driving force could be external field or concentration gradient. And the dynamics is governed by diffusion equation

\begin{align}
\frac{\partial C}{\partial t} = D \frac{\partial^2 C}{\partial x^2},
\end{align}

where C is concentration in unit of \si{mol\per cm^3}, and D is diffusion coefficient in unit of \si{cm^2\per\second}. Diffusion coefficient highly depends on the overall environments in which the ions resides. Typical values of D for Na ions are listed in Table.~\ref{tab:mona}

\begin{table}[htb]
\centering
\caption{Na diffusion coefficient ($cm^2/sec$), R is molar gas constant (8.315 \si{\joule\per mol\per K}), and T is temperature in K}\label{tab:mona}
\begin{tabular}{lcr}
\toprule
 Composition & Value  & Reference  \\
\midrule
Quartz      & $3.8\times10^{-2}exp(\frac{-24500}{RT})$  & \cite{Rybach1967a}  \\
Sodalite      & $6.6exp(\frac{-42500}{RT})$  & \cite{Sippel1963}  \\
Obsidian     & $4.4\times10^{-2}exp(\frac{-22900}{RT})$  & \cite{Sippel1963}  \\
silicate glass & $3.1\times10^{-8}$ at 420\si{\degreeCelsius} & \cite{Jbara1995} \\
\ce{SiO2} glass & $1.1\times10^{-7}$ at 670\si{\degreeCelsius} &  \cite{FRISCHAT1968}\\
\bottomrule
\end{tabular}
\end{table}

We also would like to mention the gradient of Gibbs free enthalpy overruled the concentration of a particular species, and higher \ce{OH^-} contents tend to reduce Na diffusivity.\cite{Materials2012}  The substrates used in this work are glass and ITO/glass. Related parameters is as following:
\begin{itemize}
\item dimension: $25mm\times10mm\times1mm$
\item density: 2.567 \si{g\per cm^3}
\item Na concentration: 0.01 \si{mol\per cm^3}
\item D: $1.1\times10^{-7}$ \si{cm^2\per\second}
\end{itemize}

Then the net flux $J$ is estimated as
\begin{align}
J = -D \frac{\Delta C}{\Delta x} = 2.0e^{-8} mol/cm^2/sec,
\end{align}

for a typical 2hrs growth, the net amount of Na diffusing out of substrate is then 144$\mu mol$, about 10\% of total Na ions. The diffusion length $\sqrt{Dt}$ is 190 $\mu m$. We noticed this result overestimate since the flux will reduce gradually. Meanwhile the molar amount of \ce{NaOH} applied on Si substrate is about 1$\mu mol$. Considering the adjusted ratio, Na contents should be much more when using glass substrate than when using NaOH-Si substrate.

Another important factor is the evaporation of sodium molybdates. However, few report could be found in literature. We only find one by \citeauthor{Kazenas2010}.\cite{Kazenas2010} The partial pressure\footnote{$logP(atm)= -13794/T + 6.19$} of \ce{Na2MoO4} is calculated to be 0.2 mTorr at 800 \si{\degreeCelsius} and $3.5\times 10^{-3}$ mTorr at 670 \si{\degreeCelsius}.

\begin{table}[htb]
\centering
\caption{Reactants list}\label{tb:source}
\begin{tabular}{lcccr}
\toprule
Material & Stock No & LOT &Purity & Vendor\\
\midrule
\ce{NaOH}        & S318-500 & 070241 & 99.8\% & Fisher Scientific \\
\ce{NaI}        & 11665 & K11W054 & 99.9\% &  Alfa Aesar \\
\ce{KI}        & 42857 & H06Z051 & 99.9\% &  Alfa Aesar \\
\ce{Na2CO3}        & 33377 & 114X012 & 99.95\% &  Alfa Aesar \\
\ce{Molybdenum}        & 00932 & I07S024 & 99.9\% &  Alfa Aesar\\
\bottomrule
\end{tabular}
\end{table}

\textbf{tower-like structure}

Nanotower is a less common morphology in the structures of nanomaterials.\cite{Kharissova2010} We have not found report on  \ce{MoO3} nanotower structures, although there are several studies on \ce{In2O3},\cite{Jean2010,Yan2007}, GaN\cite{Xiao2012} and ZnO\cite{Zhang2013c}. \citeauthor{Jean2010} investigated the growth mechanism of \ce{In2O3} nanotowers and attributed it to the periodical axial and continuous lateral growth interaction, where the former was first guided by Au-In alloy liquid, and subsequent by self-catalytic In droplets (MP 156C) while the latter due to VS process. In contrast, \citeauthor{Yan2007} observed similar \ce{In2O3} nanotower growth and proposed that the axial growth is controlled by Au-catalytic VLS process. \citeauthor{Xiao2012} reported the GaN nanotower grown on Ni-coated Si(111) substrates and explained the growth as asymmetric self-copy process based on VLS mechanism. \citeauthor{Zhang2013c} studied the growth of ZnO nanotower and provided a competitive model between axial and lateral growth controlled by Zn vapor to explain the as-synthesized structures. (When ZnO and carbon mixture was used as source instead of ZnO alone, nanorods array results, presumably due to the stable supply of Zn vapor owing to the gentle carbothermal reduction.) Therefore the fluctuation of reagents is probably responsible for tapering and periodical modification, which is absent in the coin roll style growth of \ce{MoO3} tower on Si. The occasionally observed tapering or enlarging on \ce{MoO3} tower can be attributed to the cooling down growth.  An oxygen regulated growth will be conducted to reveal the role of vapor pressure during the formation of tower.

long belts  is also found on Mica(\ce{K(Al2)(Si3Al)O10(OH)2}), the formation probably arise from Potassium-catalyzed VLS mechanism.\cite{Hu2011}

\subsubsection{time stepwise growth}

With time stepwise growth, the following results were obtained:

\begin{enumerate}
\item When no Mo powder is used, NaOH still hold onto substrate with some locations exhibiting etching.
\item When no Mo powder is used while growth is performed in an old tube or oxygen flow is limited to a extreme small value, circular droplet-like solid were found and Mo, Na and O were detected, suggesting the existence of VLS mechanism. Using Moly coated substrate and subsequent NaOH treatment, similar droplets formation was repeated. No discernible XRD pattern emerged, illustrating the amorphous nature of liquid catalyst.
\item 1mins growth shows plates in high temp end and irregular shapes in low temp end.
\item 15mins growth shows \ce{MoO3} plates parallel to substrate, with some belts emerging and growing out of the substrate plane. This is presumably due to the growth direction mismatch between different plates. Morphology will also depend on local NaOH concentration. NaOH trace mark turns into connected plates at the original locations, showing the high concentration mediated the morphology evolution. The possible catalyst solid was sitting on the top of plate layer. Also some belt-like growth is visible on reaction chamber walls, suggesting the evaporation and transport of \ce{NaxMoO3} vapor phase;
\item 30mins growth:  belts growth begin (500 microns long, grow rate is estimated to be 0.5 $\mu m/s$), tower structures show up as well, but much less than belt. Two kinds of belts found, tapering and non-tapering. The former one seems to have droplets mostly associated with sidewalls of the top part.
\item In reduced time or less oxygen supply growth, Na-containing site was found located onto the sidewall of belts instead of the usual expected tip. XRD pattern indicated the existence of \ce{NaxMoO3} phase. And MoO3 XRD pattern is dominated by (0k0) peaks, indicating a 2D layer-by-layer growth with lateral rate exceeding that of axial direction.
\item 2hr growth: there are crossed tapering belts at downstream boundary, with more than one droplet located along the interface of two perpendicular belts, EDX confirmed high Na content.
\item The tower is paled along $\langle010\rangle$ direction, and the belt growth direction is $\langle001\rangle$.
\item Using NaOH treated hydrophobic substrates, dense tower array growth was found along the edge areas or molten periphery of droplets, where 5 mins growth already show the initial stage of tower with diameter about 1 $\mu m$, which increase to 10 $\mu m$ in prolonged growth.
\end{enumerate}

We divide the growth into two stages according to the emerging time of long belts and towers. In first stage the growth is dominated by lateral growth, as illustrated in . In the second stage, \ce{NaxMoO3} is evaporated and recondensed in the low temperature region, and some droplet will form, and when at proper locations, introduce secondary VLS growth.

In first stage, the Na-Mo-O liquid is formed and have much more higher absorption rate than that of bare substrate. The absorbed species will diffuse along the surface and inside the liquid. It was difficult to estimate which diffusion path one is faster. When the size of liquid is smaller than some critical size, there is no preferred growth direction. This changed when the precipitated solid exceeds certain critical dimension, and the morphology evolution is then determined by the relative size of already formed solid and its liquid catalyst.

The overall reactions probably occur in the following sequences.
First, Mo powder is oxidized and \ce{MoO3} vapor is produced and transported to downstream by Ar carrier gas. Then,
\begin{align}
\cee{NaOH(l) + MoO3(g) -> Na2MoO4(l) + H2O(g)}
\end{align}

The melting point of \ce{Na2MoO4} is 687 \si{\degreeCelsius}. Based on the open air temperature profile (Fig.~\ref{fig:mooxgrowth}), the substrate is locate in temperature zone between 650 and 400 \si{\degreeCelsius}. The temperature distribution is different due to both the sealed condition and thermal conduction along the Si substrate. It will be difficult to acquire the accurate values along the substrate. However by considering the flow rate, the actual temperature will be higher than predicted by open air measurement.\cite{Subannajui2010} The melting of \ce{Na2MoO4} is highly possible when taking into account of its size as well. \cite{Bruggemann1997}

\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{Na2MoO4_Phase}
\caption[Phase diagram of Na-Mo-O]{Phase diagram of \ce{Na2MoO4} and \ce{MoO3} reproduced from ref.~\cite{Hoermann1929}}
\label{fig:pd}
\end{figure}

According to the phase diagram shown in Fig.~\ref{fig:pd}, \ce{Na2MoO4} - \ce{MoO3} phase above 800 \si{\degreeCelsius} are \ce{Na2MoO4}(l) + \ce{MoO3}(l), More discussion should follow $\ldots$.

>>>>

\documentclass[12pt,oneside]{book}
 %
   \usepackage{uncc-thesis} % some format specifications define page number in up right corner
   \input{package.tex} % additonal packages and tweaking

   \newacronym{cvd}{CVD}{chemical vapor deposition}
   \newacronym{cft}{CFT}{crystal-field theory}

   \makeglossaries

\begin{document}

  \title{\LaTeX is great}
  \author{me}
  \maketitle

    \clearpage
    \tableofcontents
    \clearpage
    \listoftables
    \clearpage
    \listoffigures

    \begin{singlespace}
    %\thispagestyle{myheadings} % before, this does not work
    \renewcommand{\glossarypreamble}{\thispagestyle{myheadings}} % after, this works.
    \printglossary[type=\acronymtype]
    \clearpage
    \end{singlespace}

 %   \include{./ch-intro/ch-intro}

After 20 minutes sonication, the dispersion is milky. We measured the transmission spectra of this dispersion immediately upon sonication and after 40 hrs for gravity sedimentation, as illustrated in Fig.~\ref{fig:moabs}. The t0 line mainly arises from the scattering of flakes in the dispersion. There are two scattering mechanisms: Rayleigh scattering and Tyndall scattering. Rayleigh scattering, which occurs when particles are comparable to wavelength, is inversely proportional to the fourth power of wavelength; While Tyndall scattering, which occurs when the particles are larger, is inversely proportional to the square of the wavelength. To fully evaluate the true absorbance of the sample itself, one needs to decouple the scattering part from apparent absorbance. Generally we select one part of spectrum and assume it is only caused by scattering. Then a empirical dependence shown in Eq.~\ref{eq:sca2} is used as polynomial fitting model.

@@

\begin{itemize}
\item s inversely proportional to the fourth
\item  inversely proportional to the fourth
\item s inversely proportional to the fourth
\end{itemize}

\begin{figure}[htb]
\centering
\subcaptionbox{\label{fig:moind}}{\includegraphics[width=0.35\linewidth]{n_MoO3}}%
\subcaptionbox{\label{fig:mocon}}{\includegraphics[width=0.55\linewidth]{Graph20}}
\caption[Refractive indices of \ce{MoO3}]{(a) Refractive indices of \ce{MoO3} Dashed line is n along $a$ axis while solid line is along $c$ axis. (b) optical contrast mapping of 1L \ce{MoO3} on \ce{SiO2}-Si. The x axis is \ce{SiO2} thickness, y axis is wavelength.It is assumed that the incident light is polarized along c axis of \ce{MoO3}.}
\label{fig:mofl}
\end{figure}
%[width=0.45\textwidth]

Rayleigh scattering and Tyndall scattering. Rayleigh scattering, which occurs when particles are comparable to wavelength, is inversely proportional to the fourth power of wavelength; While Tyndall scattering, which occurs when the particles are larger, is inversely proportional to the square of the wavelength. To fully evaluate the true absorbance of the sample itself, one needs to decouple the scattering part from apparent absorbance. Generally we select one part of spectrum and assume it is only caused by scattering. Then a empirical dependence shown in Eq.~\ref{eq:sca2} is used as polynomial fitting model.

   %\glsaddallunused
    \appendix
    \chapter{math}
    \renewcommand{\bibname}{REFERENCES}
    \begin{singlespace}
    \printbibliography
    \end{singlespace}

\end{document}
